---
title: "CPTED/Byrne Analysis"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r init}
# Initialize
## packages
library(tidyverse)
library(haven)
library(magrittr)
library(Hmisc)
library(forcats)
library(stringr)
```

# Survey Outcomes

```{r}
# data sources
nls <- read_spss("U:/HBHE/PRC/Projects/Flint Byrne/Data/Survey/2014-2016-2017_Byrne Analyses/Merged Data & Final Analyses/2014-2016-2017 merged datav1_3.sav")

# rename quality of life column
colnames(nls)[13] <- "NSQOL"

# clean Survey_Wave
nls$Survey_Wave <- nls$Survey_Wave %>%
  as.factor() %>%
  fct_recode(`2014` = "1", `2017` = "3")

# clean Study_Condition
nls$Study_Condition <- nls$Study_Condition %>%
  as.factor() %>%
  fct_recode(C = "1", `C+B` = "2", Comp = "3")
```

### Plot of Survey Outcomes

```{r, fig.width=7}
# summarise means for each group
nls_means <- nls %>%
  group_by(Study_Condition, Survey_Wave) %>%
  summarise(
    NSQOL            = mean(NSQOL, na.rm = T),
    SocCapCo         = mean(SocCapCo, na.rm = T), 
    YouthEmpower     = mean(YouthEmpower, na.rm = T), 
    FoC              = mean(FoC, na.rm = T), 
    NHPart           = mean(NHPart, na.rm = T), 
    NeighborRelation = mean(NeighborRelation, na.rm = T),
    NHDis            = mean(NHDis, na.rm = T),
    PolicePercep     = mean(PolicePercep, na.rm = T),
    PoliceRelation   = mean(PoliceRelation, na.rm = T),
    Victim           = mean(Victim, na.rm = T),
    Parks            = mean(Parks, na.rm = T),
    MentalHealth     = mean(MentalHealth, na.rm = T)
  ) %>%
  ungroup() %>%
  filter(Survey_Wave != 2) %>%
  gather(key = "Variable", value = "Group Mean", -c(Study_Condition, Survey_Wave))

# plot means
nls_means_plots <- nls_means %>% 
  ggplot(aes(x = Study_Condition, 
             y = `Group Mean`, 
             fill = factor(Survey_Wave))
         ) + 
  geom_col(position = "dodge") +
  facet_wrap(~Variable) +
  labs(
    x = "Study Condition",
    fill = "Survey Wave"
  )

# print plot
nls_means_plots
```

### Summary of Two-way ANOVA

|Scale                        |Condition       |Wave        |Condition x Wave |
|-----------------------------|:--------------:|:----------:|:---------------:|
|Neighborhood Quality of Life |`***`           |            |                 |
|Social Capital and Cohesion  |                |            |                 |
|Fear of Crime                |`***`           |`***`       |                 |
|Neighborhood Participation   |                |`*`         |.                |
|Neighborhood Disorder        |`***`           |`***`       |                 |
|Police Perception            |`***`           |`***`       |                 |
|Police Relations             |`**`            |`**`        |`*`              |
|Victimization                |                |`**`        |                 |
|Parks                        |`***`           |`***`       |                 |
|Mental Health                |                |            |                 |


### Two-way ANOVA (on Study Condition and Survey Wave)

```{r}
# Run two way ANOVA models to see if there were significant differences in resident perceptions by study condition. Outcome variables are the scales from the NLS survey, factor variables are the Study_Condition and the Survey_Wave. So, did the intervention have an impact on the mean levels of resident perceptions?

# select columns, melt data
nls_anova_data <- nls %>%
  select(
    Survey_ID,
    NSQOL,  
    SocCapCo,      
    YouthEmpower,     
    FoC,           
    NHPart,    
    NeighborRelation,
    NHDis,     
    PolicePercep,    
    PoliceRelation,  
    Victim,    
    Parks,
    MentalHealth,
    Study_Condition,
    Survey_Wave
  ) %>%
  gather(key = "nls_scale", value = "value", -c(Survey_ID, Study_Condition, Survey_Wave)) %>%
  filter(Survey_Wave != 2)

# create vector of scales
scales <- c("NSQOL", 
            "SocCapCo", 
            #"YouthEmpower",    Missing data on first wave
            "FoC", 
            "NHPart", 
            #"NeighborRelation", Missing data on first wave and C+B condition
            "NHDis",
            "PolicePercep", 
            "PoliceRelation", 
            "Victim", 
            "Parks", 
            "MentalHealth")

# loop over scale names and run two-way anova
nls_models <- sapply(scales, function(x){
  lm(value ~ Study_Condition + Survey_Wave + Study_Condition*Survey_Wave, 
     data = nls_anova_data, 
     nls_scale == x)
}, simplify = F)

# run anova without interaction term for pairwise comparison
nls_pairwise <- sapply(scales, function(x){
  aov(value ~ Study_Condition + Survey_Wave, 
     data = nls_anova_data, 
     subset = nls_scale == x)
}, simplify = F)

# summarise output
nls_ANOVA_tables <- sapply(nls_models, anova, simplify=FALSE)

# post-hoc testing
nls_pairwise_tables <- sapply(nls_pairwise, TukeyHSD, simplify=FALSE)

# print output
nls_ANOVA_tables
nls_pairwise_tables
```

# PMOT Outcomes

```{r}
# import/clean data
pmot <- read_spss("U:/HBHE/PRC/Projects/Flint Byrne/Data/Parcel Assessments/Analyses/2014-2017 Merge/Byrne14-17_PMOT_Merge_Final.sav")

## create df for each year
### 2014
pmot.2014 <- pmot %>% 
  select(Parcel_ID:Census_Tract_2010, 
         Assess_Year_2014:General_Parcel_Blight_Index_2014)

colnames(pmot.2014) <- colnames(pmot.2014) %>% str_replace("_2014", "")

### 2015
pmot.2015 <- pmot %>% 
  select(Parcel_ID:Census_Tract_2010, 
         Assess_Year_2015:General_Parcel_Blight_Index_2015)
colnames(pmot.2015) <- colnames(pmot.2015) %>% str_replace("_2015", "")

### 2016
pmot.2016 <- pmot %>% 
  select(Parcel_ID:Census_Tract_2010, 
         Assess_Year_2016:General_Parcel_Blight_Index_2016)
colnames(pmot.2016) <- colnames(pmot.2016) %>% str_replace("_2016", "")

## bind pmots
pmot <- bind_rows(pmot.2014, pmot.2015, pmot.2016, .id = "Year")

pmot <- pmot %>%
  mutate(
    Year = factor(Year),
    Year = fct_recode(Year, "2014" = "1", "2015" = "2", "2016" = "3")
  )

# select columns
pmot <- pmot %>%
  select(Year, Study_Condition, Building_Maintenance_Scale, Lawn_Maintenance_Scale, General_Parcel_Maintenance_Scale, Building_Blight_Index, Lawn_Blight_Index, General_Parcel_Blight_Index)
```

### Plot of Property Assessment Outcomes

```{r, fig.width=7}
# summarise means for each group
pmot_means <- pmot %>%
  group_by(Study_Condition, Year) %>%
  summarise(
    Building_Maintenance       = mean(Building_Maintenance_Scale, na.rm = T),
    Building_Blight            = mean(Building_Blight_Index, na.rm = T),
    Lawn_Maintenance           = mean(Lawn_Maintenance_Scale, na.rm = T),
    Lawn_Blight                = mean(Lawn_Blight_Index, na.rm = T),
    General_Parcel_Maintenance = mean(General_Parcel_Maintenance_Scale, na.rm = T),
    General_Parcel_Blight      = mean(General_Parcel_Blight_Index, na.rm = T)
  ) %>%
  ungroup() %>%
  filter(Study_Condition != 9) %>%
  gather(key = "Variable", value = "Group Mean", -c(Study_Condition, Year)) %>%
  mutate(
    Year = as.numeric(Year),
    Year = (Year + 2013),
    Study_Condition = as.factor(Study_Condition),
    Study_Condition = fct_recode(Study_Condition, C = "1", `C+B` = "2", Comp = "3")
  )

# plot means
pmot_means_plots <- pmot_means %>% 
  ggplot(aes(x = Year, y = `Group Mean`, color = factor(Study_Condition))) + 
  geom_line() +
  geom_point()+
  scale_x_continuous(limits = c(2013.5, 2016.5), breaks = c(2014, 2015, 2016)) +
  facet_wrap(~Variable) +
  labs(
    x = "Year",
    color = "Study Condition"
  )

# print plot
pmot_means_plots
```

### Summary of Two-way ANOVA

|Scale                        |Condition       |Year        |Condition x Year |
|-----------------------------|:--------------:|:----------:|:---------------:|
|Building Maintenance         |`***`           |`**`        |`*`              |
|Lawn Maintenance             |`***`           |`***`       |`**`             |
|Property Maintenance         |`***`           |            |`**`             |
|Bulding Blight               |`***`           |`**`        |`**`             |
|Lawn Blight                  |`***`           |`***`       |`***`            |
|Property Blight              |`***`           |`***`       |`***`            |

### Two-way ANOVA (on Study Condition and Year)

```{r}
# Run two way ANOVA models to see if there were significant differences in property maintenence by survey year. Outcome variables are the scales and indeces for property assessment, factor variables are the Study_Condition and the Year. So, did the intervention have an impact on the mean levels of resident perceptions?

# select columns, melt data
pmot_anova_data <- pmot %>%
  select(
    Year, 
    Study_Condition, 
    Building_Maintenance_Scale, 
    Lawn_Maintenance_Scale, 
    General_Parcel_Maintenance_Scale, 
    Building_Blight_Index, Lawn_Blight_Index, 
    General_Parcel_Blight_Index
  ) %>%
  gather(key = "pmot_scale", value = "value", -c(Study_Condition, Year)) %>%
  filter(Study_Condition != 9, !is.na(value)) %>%
  mutate(Study_Condition = as.factor(Study_Condition))

# create vector of scales
scales <- c("Building_Maintenance_Scale", 
            "Lawn_Maintenance_Scale", 
            "General_Parcel_Maintenance_Scale", 
            "Building_Blight_Index", 
            "Lawn_Blight_Index", 
            "General_Parcel_Blight_Index")

# loop over scale names and run two-way anova
pmot_models <- sapply(scales, function(x){
  lm(value ~ Study_Condition + Year + Study_Condition*Year, 
     data = pmot_anova_data, 
     pmot_scale == x)
}, simplify = F)

# run anova without interaction term for pairwise comparison
pmot_pairwise <- sapply(scales, function(x){
  aov(value ~ Study_Condition + Year, 
     data = pmot_anova_data, 
     subset = pmot_scale == x)
}, simplify = F)

# summarise output
pmot_ANOVA_tables <- sapply(pmot_models, anova, simplify=FALSE)

# post-hoc testing
pmot_pairwise_tables <- sapply(pmot_pairwise, TukeyHSD, simplify=FALSE)

# print output
pmot_ANOVA_tables
pmot_pairwise_tables
```

# Injury Outcomes

```{r}

```

# Crime Incidence Outcomes

```{r, eval = F}
crime <- read_spss("U:/HBHE/PRC/Projects/YVPC 2000-2005/Crime Data/Jianan's Working File/2015 Flint/2015 Crime Data/Flint_Crime_Data_2015.sav")

crime_geo <- crime %>%
  filter(!is.na(LATITUDE), !is.na(LONGITUDE)) %>%
  as.data.frame()

coordinates(crime_geo) <- ~LONGITUDE+LATITUDE
```










